The K2 Bright Star Survey

### 2019-05-17 paper/ms.tex
last paragraphs

% halo method

>>>>

% halo method
There are directions for improvement of the halo method itself, and for applying it beyond \kepler/\ktwo and TESS. It remains to be seen how well the method of optimizing convex objective functions can deal with significantly varying PSFs, such as from ground-based observations. The rapidly varying and moving seeing-limited PSF couples to flat field errors as is the case with \kepler, and leads to severe short-timescale instrumental noise. Self-calibration by the halo method, or a similar method, may permit improvements in ground-based photometry. Likewise, there may be other convex objective functions, including linear combinations of currently-used objective functions, which offer superior performance, for example by using combinations of different lagged functions to suppress systematics occurring at different timescales. The remaining unexplored space of convex objective functions suitable may offer significant improvements on existing self-calibration techniques in high-cadence photometry and related problems in astronomy.
